### 2013-09-13 chi2014/method.tex
typo

If an idea \emph{A} is a parent of idea \emph{B}, A is a generalization of B: all ideas in A are are suitably general to encompass all ideas in B. This difference is relative to the ideas in question.

>>>>

If an idea \emph{A} is a parent of idea \emph{B}, A is a generalization of B: all instances in A are are suitably general to encompass all instances in B. This difference is relative to the ideas in question.
